---
title: "Linear Regression"
author: "Yuhong"
date: "2023-08-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
library(readr)
train<-read_csv('/Users/yuhongchen/Desktop/work/summer intern/Group/Cross Selling/Train.csv')
```
```{r}
head(train)
```

#Null model
```{r}
n0 <- lm(formula = ind_cco_fin_ult1 ~1, data=train)
summary(n0)
```

#One explanatory variable
```{r}
m1<-lm(formula=ind_cco_fin_ult1 ~ sexo,data=train)
summary(m1)
```


#Multiple regression
```{r}
m2<-lm(formula=ind_cco_fin_ult1 ~ sexo+age+antiguedad,data=train)
summary(m2)
```

#With other terms
```{r}
m3<-lm(formula=ind_cco_fin_ult1 ~ age+antiguedad,data=train)
summary(m3)
```
#With other terms
```{r}
m4<-lm(formula=ind_cco_fin_ult1 ~ sexo+antiguedad,data=train)
summary(m4)
```
#Test the AIC
```{r}
AIC(n0,m1,m2,m3,m4)
```

So we can see that m2<-lm(formula=ind_cco_fin_ult1 ~ sexo+age+antiguedad,data=train) is the final model.
On whether the terms influence the selling of current account. 
On the model the terms of m2 model has viewed the AIC and the terms are the relatively independent terms that 
influence selling of current accoung significantly.
So under these, company could use the terms of customers to improve the cross selling upon this one account.
And also find the same significant terms between different accounts or products, which could realize the corss selling improvement. One product, Two product, or even 3 or 4, they have the same terms in models influencing significantly of the selling of them, then the business advisors could take more attention on these terms, like age, province or else.




